---
title: "Untitled"
output: html_document
author: Felicity
date: 08/APR/2020
---

# Title Learning to use R markdown
create some **bold** text or in _italics_

note you need a blank line between text otherwise it will wrap it onto the same line

```
a block of code that is not activated
```

1. text 1
2. text 2
3. text 3

* text 1
* text 2
* text 3

## 2nd level header Initialisation: Load the libraries

test

### Hide the messages uses message FALSE

```{r, message=FALSE}
library(tidyverse)
```


## 2nd level header Data Manipulation: Loading the data and filtering for Australia only

test

### run the code using results hide - doesn't show the print to screen dataframe

```{r, results='hide'}

gapminder <- read_csv("data/gapminder_data.csv")
gapminder_australia <- filter(gapminder, country == "Australia") #filter to get the Australian only data
gapminder_australia #print the dataframe to the screen

```

### 3rd level header Plotting: Creating a graph of Australian population over time

```{r}
ggplot(gapminder_australia, aes(x= year, y = pop))+
  geom_point()+
  geom_line()+
  labs(title = "Australian population over time")
```

